\documentclass{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
%
%
%
\begin{document}%
\normalsize%
\section{Personal Information}%
\label{sec:PersonalInformation}%
Name: Divya Patel%
\linebreak%
Location: Canada%
\linebreak%
Phone: 437{-}799{-}2908%
\linebreak%
Email: divyapatel4572@gmail.com%
\linebreak%
GitHub: github.com/DivyaPatel304%
\linebreak%
LinkedIn: linkedin.com/in/iamdivyapatel

%
\section{Work Experience}%
\label{sec:WorkExperience}%
\subsection{Cyberstrek Technologies}%
\label{subsec:CyberstrekTechnologies}%
Job Title: Web Developer (Jun 2021 {-} Jan 2023)%
\linebreak%
Location: Ahmedabad {-} India%
\linebreak%
Responsibilities:%
\linebreak%
{-} Leveraged Node.js for backend development and MySQL for database optimization to boost server{-}side processes by 40\% and elevate application performance by 30\%.%
\linebreak%
{-} Directed the entire process from gathering client requirements to crafting tailored solutions, deploying, monitoring, and debugging multiple web applications.%
\linebreak%
{-} Sustained ongoing support for 20 web applications, ensuring 95\% client satisfaction through rapid issue resolution.%
\linebreak

%
\subsection{Euroteck India}%
\label{subsec:EuroteckIndia}%
Job Title: Software Developer {-} Internship (Dec 2021 {-} May 2021)%
\linebreak%
Location: Ahmedabad {-} India%
\linebreak%
Responsibilities:%
\linebreak%
{-} Developed an advanced ERP system for Euroteck India using MySQL and Flask; increased resource allocation accuracy by 35\% and reduced inventory discrepancies by 20\%, optimizing overall workflow.%
\linebreak%
{-} Seamlessly transitioned paper{-}based workflows into the ERP within 6 months, significantly improving efficiency.%
\linebreak%
{-} Advanced continuous improvement processes by regularly updating based on comprehensive bug analytics and client feedback, resulting in a 70\% reduction in client{-}reported issues.%
\linebreak

%
\section{Projects}%
\label{sec:Projects}%
Music Recommendation System |Python, TensorFlow, Flask Feb 2024 {-} Apr 2024 {-}Built a music recommendation system using Python and TensorFlow, handling a database of 120,000+ songs with recommendations generated in just 300ms. {-}Implemented content{-}based filtering and cosine similarity for tailored song recommendations. Georgian College Auto Show |React Native, Firebase, Google Maps API May 2023 {-} Aug 2023 {-}Led the development of an advanced mobile app for Georgian College’s auto shows using React Native, Firebase, and Google Maps API, featuring dynamic ticketing, interactive location viewing, and real{-}time event notifications. {-}Maintained proactive client communication to ensure alignment and successful project deployment. Push Notification Platform |Node.js, React.js, Google Firebase May 2021 {-} Aug 2021 {-}Developed an innovative SaaS push notification platform using PHP, Next.js, and Google Firebase Cloud Messaging, designed to deliver targeted notifications efficiently. {-}Achieved under 100 milliseconds latency and over 98\% delivery success rate through optimized algorithms.%
\linebreak

%
\end{document}